This dissertation was truly a collaborative effort, and would not have come together without the support of a great number of people.

First, I would like to acknowledge my funding sources---the Boston University Department of Earth \& Environment and NASA---which allowed me to conduct my research freely and without interruption throughout my entire PhD.
This work also relied heavily on supercomupting resources provided to me free of charge by Boston University.

I would also like to thank all of my fellow graduate students at Boston University, both in Earth \& Environment and in Biology,
and particularly those in my year---Andrew Trlica, Paulo Arevalo, and Radost Stanimirova---for your intellectual and emotional support throughout my dissertation.
Thank you, too, to Amy Zanne, Amy Milo, and Marissa Lee for adopting me into your lab when I moved to the Washington, DC area,
and for providing me with extensive feedback and support.
And of course, a particularly warm thank you to past and present members of the Ecological Forecasting lab for your significant intellectual input, and for making my day-to-day routine better. 

A sincere thank you goes out to my dissertation readers---Diane Thompson, Mark Friedl, and Curtis Woodcock---for your helpful feedback on this dissertation at its various stages.
I owe a particularly large debt of gratitude to Shawn Serbin for not only providing the inspiration for a lot of this PhD research, but also for providing openly and unconditionally most of the data for the later chapters and for always being available to answer my questions and provide input on results.
I am also forever grateful to my advisor Michael Dietze for fundamentally revolutionizing the way I think about and perform the scientific process, and for expertly guiding me throughout every step of the PhD process.

Finally, I wanted to thank my family for challenging and supporting me throughout my entire life, and to my fiancee Sarah Weiskopf for basically everything good that has happened to me in the last 7 years.

\vskip 1in

\noindent
Alexey Shiklomanov\\
PhD Candidate\\
E\&E Department
